\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}
\usepackage{url}
\usepackage{xurl}
\usepackage{xcolor}

\begin{document}

\begin{center}
{\LARGE\bfseries Title Page}
\end{center}

\vspace{1em}
\noindent\textbf{Manuscript title:}\\
VEIN: On-Chain Causal Risk Attribution for Cryptocurrency Systemic Risk

\vspace{1em}
\noindent\textbf{Authors (in submission-system order):}\\
1. Quang-Vinh Dang --- British University Vietnam, Hung Yen, Vietnam

\vspace{1em}
\noindent\textbf{Corresponding author:}\\
Quang-Vinh Dang, British University Vietnam, Hung Yen, Vietnam.
E-mail: \href{mailto:vinh.dq4@buv.edu.vn}{vinh.dq4@buv.edu.vn}

\bigskip
\hrulefill

\vspace{1.5em}
\begin{center}
{\LARGE\bfseries Author's Information}
\end{center}

\vspace{1em}
\noindent\textbf{Quang-Vinh Dang.}\quad
Quang-Vinh Dang is a Lecturer at British University Vietnam and Data/AI
Director at SmartOSC, where he leads initiatives in multi-agent AI systems,
large language models, and graph neural networks across banking, retail, and
finance. He holds a Ph.D. in Computer Science from Universit\'e de Lorraine
(LORIA), France (2018), an M.Sc. in Financial Engineering from WorldQuant
University (2021), and completed a Post-Master programme in Software
Technology at Eindhoven University of Technology. His research spans machine
learning in finance, natural language processing, intrusion detection, and
federated learning, and he has authored more than 60 peer-reviewed papers
indexed in Scopus/SCI-E, many in Q1 journals. Prior to his current roles, he
held data-leadership positions at Trusting Social, Be Group, GoTymeX, and
DatVietVAC, and was a postdoctoral researcher at Inria, France.

\bigskip
\hrulefill

\vspace{1.5em}
\begin{center}
{\LARGE\bfseries Cover Letter}
\end{center}

\vspace{1em}
\noindent Quang-Vinh Dang\\
British University Vietnam\\
Hung Yen, Vietnam\\
\href{mailto:vinh.dq4@buv.edu.vn}{vinh.dq4@buv.edu.vn}

\vspace{1em}
\noindent The Editor\\
\emph{Financial Innovation}

\vspace{1em}
\noindent Dear Editor,

\vspace{0.5em}
I am pleased to submit my manuscript, \textbf{``VEIN: On-Chain Causal Risk
Attribution for Cryptocurrency Systemic Risk,''} for consideration as a
research article in \emph{Financial Innovation}.

The paper proposes VEIN (Verifiable Entity-resolved Interventional/counterfactual
Network risk), a framework that treats the resolved on-chain transaction ledger
as an auditable candidate structural skeleton for a Pearl-style structural
causal model of cryptocurrency systemic risk, rather than inferring the
contagion graph statistically from price co-movement as prior causal measures
do. On this graph the paper defines an interventional risk measure (On-Chain
Causal CoVaR) and, to the best of our knowledge, the first on-chain
counterfactual (Pearl Level-3) systemic-risk attribution measure proposed for
crypto markets, which decomposes a realised loss into the Shapley-exact share
attributable to each upstream entity's distress. The complete pipeline---a
four-tier entity-resolution layer over Dune Analytics' decoded Ethereum data,
the structural causal model, and the risk measures---is implemented and
evaluated on real on-chain data around the October 2025 cascading liquidation
event, with generality checks on the FTX (2022) and USDC/SVB (2023) stress
episodes, and is subjected to a validity and falsification battery (placebo
controls, unobserved-confounding robustness at both the coefficient and
ranking level, resolution robustness, and external validity against the
documented event narrative).

We believe this manuscript is a strong fit for \emph{Financial Innovation}'s
scope at the intersection of blockchain, computational financial intelligence,
and financial risk management and analysis. The paper combines a methodological
contribution (an exact, order-robust counterfactual attribution measure) with
an extensive real-data empirical evaluation, and reports negative and
suggestive results as candidly as positive ones.

This manuscript is original, has not been published previously, and is not
under consideration at any other journal.

Thank you for considering this manuscript. I look forward to your response.

\vspace{1.5em}
\noindent Sincerely,

\vspace{0.5em}
\noindent Quang-Vinh Dang\\
British University Vietnam

\bigskip
\hrulefill

\vspace{1.5em}
\begin{center}
{\LARGE\bfseries Declarations}
\end{center}

\vspace{1em}
\noindent\textbf{Ethical Approval and Consent to participate.} Not
applicable: this study uses only public, aggregated on-chain and market data
and involves no human subjects, human data, or animals.

\vspace{0.8em}
\noindent\textbf{Consent for publication.} Not applicable.

\vspace{0.8em}
\noindent\textbf{Availability of supporting data.} The complete
implementation, the real-data evaluation pipeline, and all result artefacts
underlying every number, table, and figure in this paper are publicly
available at
\url{https://github.com/vinhqdang/VEIN-On-Chain-Causal-Risk-Attribution-for-Cryptocurrency-Systemic-Risk}.
The repository includes the full source code, cached query results, and
scripts that reproduce every reported result. All underlying blockchain and
market data are public and were obtained from Dune Analytics
(\url{https://dune.com}), DefiLlama (\url{https://defillama.com}), and
Etherscan (\url{https://etherscan.io}); no restricted or proprietary data
were used.

\vspace{0.8em}
\noindent\textbf{Competing interests.} The author declares no competing
interests.

\vspace{0.8em}
\noindent\textbf{Funding.} No external funding supported this work.

\vspace{0.8em}
\noindent\textbf{Authors' contributions.} Q.-V.D. conceived the study,
developed the VEIN framework and its implementation, performed the data
collection and empirical analysis, and wrote the manuscript.

\vspace{0.8em}
\noindent\textbf{Acknowledgements.} Not applicable.

\vspace{0.8em}
\noindent\textbf{Authors' information (Optional).} See ``Author's
Information'' above.

\end{document}
